---
title: "R Script Documentation"
author: "Rajveer Kaur"
date: "October 5, 2026"
output: html_document
---

> **AI Assistance Declaration:** I used ChatGPT (GPT-5.6 Sol) on October 5, 2026, for suggestions about Markdown formatting, section organization, and R code-block presentation. Prompts used included requests to improve headings, syntax highlighting, and R Markdown organization. I manually reviewed the output and verified the document structure using RStudio/Posit Cloud preview. No real or personal data was provided to the AI tool. All final work was reviewed by me, and I am responsible for its accuracy and originality.

# Purpose

This R Markdown document explains a simple R script that works with a synthetic dataset. The purpose of the script is to demonstrate how data can be created, inspected, summarized, and documented clearly in an R project.

The example uses synthetic data only and does not contain personal or confidential information.

## Inputs

The script uses a small synthetic dataset created directly in R.

The dataset contains two variables:

- `category` – identifies three example categories.
- `value` – contains a numeric value for each category.

```{r create-data} id="6y7g6a"
sample_data <- data.frame(
  category = c("A", "B", "C"),
  value = c(12, 18, 15)
)
```

## View the Data

The following R code displays the synthetic dataset.

```{r view-data} id="9dptbv"
print(sample_data)
```

This allows the user to confirm that the dataset was created correctly before continuing.

## Data Structure

The `str()` function is used to inspect the structure and data types of the dataset.

```{r inspect-data} id="hhc19l"
str(sample_data)
```

This helps confirm that the variables have been stored appropriately.

## Summary

The following code produces a basic summary of the
